\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-26 draft.tex
revise first paragraph of model section to integrate numeraire

\section{The Model}
\label{sec:model}
Following the literature on the political economy of trade agreements as exemplified by Bagwell and Staiger (2005), I employ a partial equilibrium model with two countries: home (no asterisk) and foreign (asterisk). The countries trade two goods, $X$ and $Y$, where $P_i$ denotes the home price of good $i \in \left\{X,Y\right\}$ and $P_i^*$ denotes the foreign price of good $i$. In each country, the demand functions are taken to be identical for both goods, respectively $D(P_i)$ in home and $D(P_i^*)$ in foreign and are assumed strictly decreasing and twice continuously differentiable.

>>>>

\section{The Model}
\label{sec:model}
I begin by describing the basic economic setting within which trade occurs. It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In each country, preferences are linear in good $N$, which is denoted the numeraire, while the demand functions for $X$ and $Y$ are assumed strictly decreasing and twice continuously differentiable. Further, the demand functions for $X$ and $Y$ are taken to be identical and denoted $D(P_i)$ in home and $D(P_i^*)$ in foreign. $P_i$ denotes the home price of good $i \in \left\{N,X,Y\right\}$ and $P_i^*$ denotes the foreign price of good $i$.
